Appendix

### 2020-05-17 appendixupdates/appendixV4.Rmd
Original contents of appendixupdates
Version: 2020-05-14

@@

Therefore, no effects.

@@

@@

>>>>

### Meta-regressions for Expenditure as a Percentage of the GDP

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)
```

@@

We have the following results for the meta-regressions of Expenditure Per Capita:

1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
2. Year has null effect.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
```

@@

For all the coefficients, we have the following results:

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

### Meta-regressions for Expenditure Per Capita

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear)
```

We have the following results for the meta-regressions of Expenditure Per Capita:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
5. When passing from `Local` to `State` level, decreases the detected effects.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
```

With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

### Meta-regressions for the Log of Expenditure Per Capita

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
```

We have the following results for the meta-regressions of Log of Expenditure Per Capita:

1. Unpublished papers report a significantly higher coefficient.
2. In terms of the modeling, passing from `OLS` to `PANEL`increases the detected effects.
3. All other coefficients remained insignificant.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
```

With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:

1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
2. All other coefficients remained insignificant.

@@

## Robustness: Full model meta-regressions combined
